---
title: "Lab 1 Assignment"
author: 'Team #4'
date: "02/06/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1 Link to our git repo  
https://github.com/qhe0917/LAB-1-STAT-585 

## Part 2 Building a book   
Problems that came up
`Error1:` could not find certain packages.   
`Solution1:` download them, but this just can be way too much work to do. (Some packages might need to be downloaded via devtools::install_github("username/reponame")) 

`Error2:`'current-env' is not an exported object from 'namespace:rlang' Execution halted
`Solution2:` Might be issues from Rcpp compiler.


## Part 3 Weather stations   


```{r, message=F, warning=F}
library(readr)

ushcn_data <- read_fwf("ftp://ftp.ncdc.noaa.gov/pub/data/ushcn/v2.5/ushcn-v2.5-stations.txt",
                       fwf_widths(c(2,1,2,7,
                                    9,11,6,
                                    3,31,7,7,7,
                                    2),
                       c("country","network","ID","coop_ID","lat","long","elev","state","name","comp1","comp2","comp3","utc")),
                       col_types = cols('c','c','c','c','n','n','n','c','c','c','c','c','i'))

library(ggplot2)
library(ggmap)
library(maps)
states=map_data("state")
ushcn_data$utc=as.factor(ushcn_data$utc)
ushcn_data$state=as.factor(ushcn_data$state)
ushcn_data$lat = as.numeric(ushcn_data$lat)
ushcn_data$long = as.numeric(ushcn_data$long)

levels(ushcn_data$utc) <- c("EST","CST","MST","PST")
cnames <- aggregate(cbind(long, lat) ~ state, data=ushcn_data, 
                    FUN=function(x)mean(range(x)))
ggplot(data=states) + 
  geom_polygon(aes(x = long, y = lat, fill = region, group=group),col="white",alpha=0.4)+
  geom_point(data=ushcn_data,aes(x=long,y=lat,col=elev,shape=utc),size=0.8) +  
  geom_text(data=cnames, aes(long, lat, label = state), size=2) +
  theme(text = element_text(size=10))+
  guides(fill=FALSE)



```



## Part 4 More weather data
```{r, message=F, warning=F}
require(R.utils)
library(R.utils)
library(data.table)
# gunzip("ushcn.tavg.latest.raw.tar.gz")
untar("ushcn.tavg.latest.raw.tar")
file=list.files(path="ushcn.v2.5.5.20190204")
length(file)

# Fort Dodge's location 42.506803, -94.180271
# US %>% filter(Name=="Fort Dodge")
#ushcn_data %>% filter(lat> 42 & lat< 43 & long< -94 & long> -95)
#Or search the name by matching the keywords of name
ushcn_data[tolower(ushcn_data$name) %like% "fort dodge",]
#the COOPID for Fort Dodge
ID<-ushcn_data[tolower(ushcn_data$name) %like% "fort dodge",]$coop_ID
#search the file names that matchs the COOPID inside the file
file[file %like% ID]
```




Deliverable: include the number of files inside the file ushcn.tavg.latest.raw.tar.gz and the name of the file containing the temperature data of your home towns or Fort Dodge, IA (please specify).
`Solution:` There are 1218 files in total; file name, which is for Fort Dodge, is `USH00132999.raw.tavg`.



