---
title: "README"
author: 'Team #4'
date: "1/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(ggplot2)
require(tidyverse)
```

## Part 1 Link to our git repo  
https://github.com/qhe0917/LAB-1-STAT-585 

## Part 2 Building a book   
Deliverable (1): what is the last word in chapter 15? - You don't have to answer this question, if things don't work, but please answer the next one and see the next page.  
`pseudo-class` in reference.

Deliverable (2): Write a paragraph on the biggest problem you encountered when you were building the book, and how you managed to solve it.  
`Error:` could not find certain packages.   
`Solution:` download them, but this just can be way too much work to do. (Some packages might need to be downloaded via devtools::install_github("username/reponame"))   


## Part 3 Weather stations   

	Variable             Columns    Type
	----------------------------------------
	COUNTRY CODE             1-2    Character 2
	NETWORK CODE               3    Character 1
	ID PLACEHOLDERS ("00")   4-5    Character 2
	COOP ID                 6-11    Character *6
	LATITUDE               13-20    Real      **7
	LONGITUDE              22-30    Real      **9
	ELEVATION              33-37    Real      *5
	STATE                  39-40    Character *2
	NAME                   42-71    Character *30
	COMPONENT 1 (COOP ID)  73-78    Character *6
	COMPONENT 2 (COOP ID)  80-85    Character *6
	COMPONENT 3 (COOP ID)  87-92    Character *6
	UTC OFFSET             94-95    Integer   2
	-----------------------------------------

```{r, message=F, warning=F, include=F, echo=FALSE}
fwf_sample <- readr_example("fwf-sample.txt")
cat(read_lines(fwf_sample))
# You can specify column positions in several ways:
# 1. Guess based on position of empty columns
read_fwf(fwf_sample, fwf_empty(fwf_sample, col_names = c("first", "last", "state", "ssn")))
# 2. A vector of field widths
read_fwf(fwf_sample, fwf_widths(c(20, 10, 12), c("name", "state", "ssn")))
# 3. Paired vectors of start and end positions
read_fwf(fwf_sample, fwf_positions(c(1, 30), c(20, 42), c("name", "ssn")))
# 4. Named arguments with start and end positions
read_fwf(fwf_sample, fwf_cols(name = c(1, 20), ssn = c(30, 42)))
# 5. Named arguments with column widths
read_fwf(fwf_sample, fwf_cols(name = 20, state = 10, ssn = 12))

# try
US=read_fwf("ftp://ftp.ncdc.noaa.gov/pub/data/ushcn/v2.5/ushcn-v2.5-stations.txt", 
           fwf_widths(c(2,1,2,7,
                        9,11,6,
                        3,31,7,7,7,
                        2),
                      c("CountryCode","NetworkCode","ID","COOPID",
                      "Latitude","Longtitude","Elevation",
                      "State","Name","Comp1","Comp2","Comp3",
                      "UTC")
                      ),
           col_types = cols("c","c","c","c",
                    "d","d","d",
                    "c","c","c","c","c",
                    "i")
           )
# has error
head(US)
```

```{r, message=F, warning=F}
require(readr)
# vignette("readr")
# cat(read_lines("ushcn-v2.5-stations.txt"))
US=read_fwf("ftp://ftp.ncdc.noaa.gov/pub/data/ushcn/v2.5/ushcn-v2.5-stations.txt", 
           fwf_cols(CountryCode=c(1,2),Networkcode=c(3,3),ID=c(4,5),COOPID=c(6,11),
                    Latitude=c(13,20),Longitude=c(22,30),Elevation=c(33,37),
                    State=c(39,40),Name=c(42,71),Comp1=c(73,78),Comp2=c(80,85),Comp3=c(87,92),
                    UTC=c(94,95)    ),
           col_types = cols("c","c","c","c",
                    "d","d","d",
                    "c","c","c","c","c",
                    "i")
           )
str(US)
head(US,3)

state=map_data("state")
# rename the levels of time zone variable UTC
US$UTC=as.factor(US$UTC)
levels(US$UTC)=c("EST","CST","MST","PST")
ggplot(data=state,aes(x=long,y=lat)) + 
  geom_polygon(aes(group=group),col="grey",alpha=0.4)+
  geom_point(data=US,aes(x=Longitude,y=Latitude,col=Elevation,shape=UTC),size=0.8) +  
  theme(text = element_text(size=10)) 

```

Deliverable: include the code necessary to read the file and to create the plot in README.Rmd. Assume the data is in the same folder as the README.Rmd file.

## Part 4 More weather data
```{r, message=F, warning=F}
library(R.utils)
library(data.table)
# gunzip("ushcn.tavg.latest.raw.tar.gz")
untar("ushcn.tavg.latest.raw.tar")
file=list.files(path="ushcn.v2.5.5.20190204")
length(file)

# Fort Dodge's location 42.506803, -94.180271
# US %>% filter(Name=="Fort Dodge")
US %>% filter(Latitude> 42 & Latitude< 43 & Longitude< -94 & Longitude> -95)

#Or search the name by matching the keywords of name
US[tolower(US$Name) %like% "fort dodge",]

#the COOPID for Fort Dodge
ID<-US[tolower(US$Name) %like% "fort dodge",]$COOPID

#search the file names that matchs the COOPID inside the file
file[file %like% ID]
```

Deliverable: include the number of files inside the file ushcn.tavg.latest.raw.tar.gz and the name of the file containing the temperature data of your home towns or Fort Dodge, IA (please specify).
`Solution:` There are 1218 files in total; file name, which is for Fort Dodge, is `USH00132999.raw.tavg`.



